\addcontentsline{toc}{chapter}{Acknowledgments}
\thispagestyle{empty}

\vspace*{20mm}

\begin{center}
    {\usekomafont{sectioning}\usekomafont{section} Acknowledgments}
\end{center}

\vspace{10mm}

This work represents the culmination of a journey that began seven years ago—a path I have walked
with unwavering dedication, guided and upheld by the grace of God, and sustained by the
love of my family: my father Ivan, my mother Ximena, and my brothers Anthony and Christian. 
Together with the encouragement of my friends and cherished loved ones, their boundless support, 
faith in me, and warmth of affection have made this achievement possible. To them, I offer my 
deepest gratitude and say, with all my heart, "Thank you, and I love you."
\newline
\newline
I extend my sincere appreciation to the team at Helmholtz, who welcomed me into an inspiring 
community of scientists and individuals. Their brilliance, generosity, and innovative spirit 
enriched my understanding and propelled me forward each day with fresh ideas and motivation. 
A special word of thanks goes to Can Demircan, whose unwavering presence sustained me through every 
challenge of this thesis. His willingness to share his wisdom and guide me with patience and 
insight has been a gift beyond measure. I am also deeply grateful to Eric Schulz, whose 
invitation opened the door to this remarkable laboratory and its extraordinary people, setting 
the stage for this chapter of my growth. Furthermore, I wish to extend my heartfelt thanks 
to Prof. Dr. Zeynep Akata for granting me the privilege of writing this thesis under her 
esteemed faculty, an opportunity that has profoundly shaped this work.
\cleardoublepage{}
